---
title: Prof. Dr.
surname: André Calero Valdez
position: "Human-Computer Interaction and Usable Safety Engineering"
address: "Institute of Multimedia and Interactive Systems, University of Lübeck"
#phone: +1 22 3333 4444
www: calerovaldez.com
email: "andre.calerovaldez@uni-luebeck.de"
profilepic: "`r paste0('..',stringr::str_remove(here::here('data','photo.jpeg'), here::here()))`"
#twitter: sumidu
github: sumidu
googlescholar: K6EVDoYAAAAJ
#researchgate: Andre-Calero-Valdez
orcid: 0000-0002-6214-1461
#linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
documentclass: moderncv
classoption: "sans"
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage[T1]{fontenc}
  - \usepackage[sfdefault,scaled=.85]{FiraSans}
  - \usepackage{eurosym}
  - \usepackage{csquotes}
output: 
  vitae::moderncv:
    keep_tex: false
#    includes:
#      in_header: header.tex
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae) # remember to use sumidu/vitae
library(tidyverse)
library(glue)
library(here)
source(here::here("R", "getdata.R"))
library(DBI)
library(RSQLite)
library(RPostgres)

# -----
# Before trying new stuff please create a database backup from the supabase database
# R/backupPostgres.R has the code to do just that
#
# Use Beekeeper Studio or something similar to edit the PostGres database directly
# Weekly updates are released automatically using the github action.
# -----

# Load database from PostGres using Remote URL

host_name <- "aws-0-eu-central-1.pooler.supabase.com"

# These have to be defined as github secrets
db_user <- Sys.getenv("SUPABASEUSER")
db_password <- Sys.getenv("SUPABASEPW")

# This allows the cronjob to determine if the google scholar profile should be updated on cronjobs
# Sys.setenv("UPDATEGOOGLESCHOLAR" = "TRUE") # Comment this line to avoid updating every time
update_google_scholar <- Sys.getenv("UPDATEGOOGLESCHOLAR")
update_pubs <- FALSE

# 
if(str_length(update_google_scholar)>0) {
  if(update_google_scholar == "true") {
    update_pubs <- TRUE
  } 
}

# Use the postgres database
db <- dbConnect(RPostgres::Postgres(), 
                dbname = "postgres", host = host_name, port = 5432, 
                user = db_user, 
                password = db_password,
                gssencmode="disable"
                )

# Use the SQLite Local Database
# db <- dbConnect(RSQLite::SQLite(), here("data", "my_data.db"))

jobs <- tbl(db, "jobs") |> collect()
degrees <- tbl(db, "degrees") |> collect()
education <- tbl(db, "education") |> collect()
grants <- tbl(db, "grants") |> collect()
awards <- tbl(db, "awards") |> collect()
memberships <- tbl(db, "memberships") |> collect()
reviews <- tbl(db, "reviews") |> collect()
committees <- tbl(db, "committees") |> collect()
services <- tbl(db, "services") |> collect()
talks <- tbl(db, "talks") |> collect()
lectures <- tbl(db, "lectures") |> collect()
consulting <- tbl(db, "consulting") |> collect()
theses <- tbl(db, "theses") |> collect()
teaching <- tbl(db, "teaching") |> collect()
teaching_evaluations <- tbl(db, "teaching_evaluations") |> collect()
software <- tbl(db, "software") |> collect()
dbDisconnect(db)

```

```{r data_loading, include=FALSE}
lang <- "de"


scholar_profile <- get_scholar_profile(update_pubs = update_pubs)
```



# Über mich

```{r about_me, results="asis"}
pd_df <- tribble(~meta, ~input,
              "Name", "Univ.-Prof. Dr. phil. André Calero Valdez", 
              #"Geburtsdatum","22. Januar 1981",
              #"Familienstand", "verheiratet mit Eva-Maria Peters (Studienrätin)",
              #"Kinder", "Tochter (6 Jahre alt), Sohn (2 Jahre)",
              #"Adresse", "Poelring 5",
              #"", "23560 Lübeck",
              "Email", "andrecalerovaldez@gmail.com",
              "www", "www.calerovaldez.com",
              "Languages", "German (Muttersprache)",
              "",         "Englisch (fließend)",
              "",         "Spanisch (Grundkenntnisse)",
              # "test", update_google_scholar # this is to test the environment variable
              )

vitae::brief_entries(pd_df, when = meta, what = input, with = "") 
```

\vspace{1em}

## Akademische Metriken

```{r metrics, results="asis"}

my_scale <- function (space = TRUE) 
{
    out <- c(0, `Tsd.` = 1000, `Mio.` = 1e+06, `Bn.` = 1e+09)
    if (space) {
        names(out) <- paste0(" ", names(out))
    }
    out
}


fnc <- scales::label_number(accuracy=0.01,
                       scale_cut = my_scale() )

total_own_funding <- 
  grants$own_amount |> 
  str_replace_all(" Mio. ", "000000 ") |> 
  str_replace_all(",","") |> 
  str_replace_all("\\.","") |>
  str_replace_all("[- Euro]","") |> 
  as.numeric() |> 
  na.omit() |> sum() |> fnc()
  

metrics_df <- tribble(~meta, ~input,
              "Zitationen", scholar_profile$total_cites %>% as.character(),
              "h-Index", scholar_profile$h_index %>% as.character(),
              "i10-Index", scholar_profile$i10_index %>% as.character(),
              "Drittmittel", glue::glue("ca. {total_own_funding} \\euro"),
              )

brief_entries(metrics_df, when = meta, what = input, .protect = F)
```

# Berufliche Erfahrung

```{r research}

# helper functions dates ----
str_yearrange <- function(start, end, active = c(FALSE))  {
  strt <- as.character(year(start))
  nd <- ifelse(active, "heute", as.character(year(end)))
  ifelse(strt == nd, strt, paste0(strt, " -- ", nd))
}

split_description <- function(description) {
  as.vector((str_split(paste0(description,""), ";")))
}


jobs %>% 
  arrange(desc(start)) %>% 
  rowwise() |> 
  mutate(when = str_yearrange(start, end, active > 0)) |> 
  detailed_entries(
    what = name,
    when = when,
    with = with,
    where = location,
    why = split_description(description)
  )
```

# Wissenschaftliche Abschlüsse

```{r degrees}
degrees %>% 
  arrange(desc(start)) %>% 
  rowwise() |> 
  mutate(when = str_yearrange(start, end)) |> 
  detailed_entries(
    what = name,
    when = when,
    with = with,
    where = location,
    why = split_description(description)
  )
```

# Ausbildung

```{r education}
education |> 
  arrange(desc(start)) |> 
  rowwise() |> 
  mutate(when = str_yearrange(start, end)) |> 
  detailed_entries(
    what = name,
    when = when,
    with = with,
    where = location,
    why = split_description(description)
  )
```

# Bewilligte Projekte

```{r}
grants %>% 
  arrange(desc(year)) %>% 
  rowwise() |> 
  brief_entries(
    what = split_description(name), 
    when = year, 
    with = funder
    )
```


# Auszeichnungen und Preise
```{r}
awards %>% 
  arrange(desc(year)) %>% 
  rowwise() |> 
  brief_entries(what = name, when = year, with = award_source)
```

# Mitgliedschaften

```{r}
memberships %>% 
  arrange(desc(start)) %>%
  rowwise() |> 
  brief_entries(
    what = name, 
    when = "")
```

\pagebreak
# Reviews und Mitwirkung in Programmkomitees


```{r}
# split and replace to allow renaming in document
reviews %>% 
  arrange(desc(review_type), desc(citescore)) %>%
  pull(name) %>% 
  glue_collapse(sep = ", ") -> adhocs

committees %>% 
  filter(position_type == "editorial") %>% 
  pull(name) %>% 
  glue_collapse(sep = ", ") -> editorial

committees %>% 
  filter(position_type == "committee") %>% 
  pull(name) %>% 
  glue_collapse(sep = ", ")  -> committee

review_df <- data.frame() %>% 
  bind_rows(data.frame(Name = committee, Type = "Programm-komitee")) %>% 
  bind_rows(data.frame(Name = editorial, Type = "Editorial-Board")) %>% 
  bind_rows(data.frame(Name = adhocs, Type = "Adhoc Reviews"))


review_df %>% 
  rowwise() |> 
  brief_entries(what = Name, when = Type)
```

# Mitwirkung an der akademischen Selbstverwaltung

```{r}
services |> 
  arrange(desc(start)) |> 
  rowwise() |>
  detailed_entries(
    what = name,
    when = str_yearrange(start, end, active > 0 ),
    with = details,
    where = location,
    why = split_description(role)
  )
```

# Beratung
```{r}
consulting %>%
  arrange(desc(start)) %>% 
  rowwise() |> 
  detailed_entries(
    what = name,
    when = year(start),
    with = client,
    where = location,
    why = role 
  )
```

# Erfahrung in der Hochschullehre

## Lehre an der Universität zu Lübeck

```{r include=TRUE}

# SHORT VERSION 
teaching %>%
  filter(year(start) >= 2022) %>%
  arrange(desc(start)) %>% 
  rowwise() |> 
  mutate(when = str_yearrange(start, end, active > 0)) |> 
  vitae::brief_entries(
    what = name,
    when = when,
    with = ""
  )
```
## Lehre an der RWTH Aachen University
```{r include=TRUE}

# SHORT VERSION 
teaching %>%
  filter(year(start) < 2022) %>%
  arrange(desc(start)) %>% 
  mutate(when = str_yearrange(start, end, active > 0)) |> 
  rowwise() |> 
  vitae::brief_entries(
    what = name,
    when = when,
    with = ""
  )
```

\vspace{1em}
\pagebreak
# Eingeladene Vorträge

```{r invited_talks}
lectures %>% 
  arrange(desc(lecture_date)) %>% 
  detailed_entries(what = title,
                   when = glue("{month(lecture_date, abbr = FALSE, label = FALSE)}/{year(lecture_date)}"),
                   with = conference,
                   where = location,
                   why = NULL)
```

# Vorträge

```{r talks}
talks %>% 
  arrange(desc(talk_date)) %>% 
  detailed_entries(what = title,
                   when = glue("{month(talk_date, label = FALSE)}/{year(talk_date)}"),
                   with = conference,
                   where = location,
                   why = NULL)
```



# Softwareentwicklung für Forschung und Lehre

```{r software,}
software %>% 
  arrange(desc(start)) %>% 
  detailed_entries(
    what = role, when = year(start), with = c(""), where = url, why = details)
```


